A convenient, flexible and intuitive analytic expression for the metallicity-dependent cosmic star formation rate

### 2022-06-08 src/tex/ms.tex
[showyourwork]
[showyourwork] overleaf sync

%%  metallicity density distribution %%
Merging BBHs are found to form more efficiently at low metallicities e.g. \citep[e.g.][]{BelczynskiVink2010, Stevenson+2017,Mapelli2017,Chruslinska2019_effectCO}. Therefore the assumed metallicity specific star formation rate will in particular have a large impact on the inferred merger rate \citep[e.g.][]{Chruslinska2019,Chruslinska2019_effectCO, Neijssel2019, Broekgaarden+2021a}.

It is difficult to observationally constrain the shape of the metallicity density distribution over redshift (see \cite{Chruslinska2019} for an extensive overview and discussion of relevant observational caveats). Traditionally the metallicity density distribution is estimated by combining a mass-metallicity relation (MZ-relation) and a galaxy stellar mass function (GSMF) \citep[see also][]{Chruslinska+2018, Chruslinska2019_effectCO, Broekgaarden+2021a}.
Another way is to extract the metallicity density fraction from cosmological simulations \citep[e.g.]{Mapelli2017, Schneider+2017}
Alternatively, one can combine an observed star formation rate, SFR(z), like from \cite{MadauDickinson2014} or \cite{Madau+2017}, and convolve this with some belief about the shape of the metallicity density distribution, such as was was done in \cite{Neijssel+2019}.
A third option is extract this information from cosmological simulations \citep[e.g.][]{Mapelli+2017,Schneider+2017}.
In this work we provide a new fit to the \SFRDzZ based on the TNG 100 simulation \citep{Pillepich2018, Weinberger2017}.

Large uncertainties exist in the shape and redshift evolution of both \SFRDz, and  \dpdZ (see e.g. \citealt{Chruslinska2019}, \citealt{Boco2021} and \citealt{Chruslinska+2021} for an extended discussion on the metallicity dependent star formation rate density, in light of empirical data).

@@

\begin{deluxetable}{cccc}
\label{tab: fit params}
\tablecaption{Best fitting parameters for our \SFRDzZ fit to TNG100 data.}
\tablehead{\colhead{dP/dZ param.} & \colhead{best fit} & \colhead{SFRD(z) param.} & \colhead{best fit} } 
%% All data must appear between the \startdata and \enddata commands
\startdata
$\mu_0$ &  0.025 &  $a$ &  0.02 \\
$\mu_z$ &  -0.048 &  $b$ &  1.48 \\
$\alpha_0$ &  -1.767 &  $c$ &  4.45 \\
$\sigma_0$  & 1.125       &  $d$ &  5.90 \\
$\sigma_z$ &  0.048 &   \\
\enddata
%sf_a_best, sf_b_best, sf_c_best,  sf_d_best = 0.02, 1.48, 4.45, 5.90
% sf_a =0.01687063881834458, sf_b =1.4834054063851878, sf_c =4.448574027958166, sf_d =5.903964702985274

@@

>>>>

%%  metallicity density distribution %%
Merging BBHs are found to form more efficiently at low metallicities e.g. \citep[e.g.][]{BelczynskiVink2010, Stevenson+2017,Mapelli2017,Chruslinska2019_effectCO}. Therefore the assumed metallicity specific star formation rate will in particular have a large impact on the inferred merger rate \citep[e.g.][]{Chruslinska2019_obs,Chruslinska2019_effectCO, Neijssel2019, Broekgaarden+2021a}.

It is difficult to observationally constrain the shape of the metallicity density distribution over redshift (see \cite{Chruslinska2019_obs} for an extensive overview and discussion of relevant observational caveats). Traditionally the metallicity density distribution is estimated by combining a mass-metallicity relation (MZ-relation) and a galaxy stellar mass function (GSMF) \citep[see also][]{Chruslinska+2018, Chruslinska2019_effectCO, Broekgaarden+2021a}.
Another way is to extract the metallicity density fraction from cosmological simulations \citep[e.g.]{Mapelli2017, Schneider+2017}
Alternatively, one can combine an observed star formation rate, SFR(z), like from \cite{MadauDickinson2014} or \cite{Madau+2017}, and convolve this with some belief about the shape of the metallicity density distribution, such as was was done in \cite{Neijssel+2019}.
A third option is extract this information from cosmological simulations \citep[e.g.][]{Mapelli+2017,Schneider+2017}.
In this work we provide a new fit to the \SFRDzZ based on the TNG 100 simulation \citep{Pillepich2018, Weinberger2017}.

Large uncertainties exist in the shape and redshift evolution of both \SFRDz, and  \dpdZ (see e.g. \citealt{Chruslinska2019_obs}, \citealt{Boco2021} and \citealt{Chruslinska+2021} for an extended discussion on the metallicity dependent star formation rate density, in light of empirical data).

@@

\begin{deluxetable}{cccc}
\label{tab: fit params}
\tablecaption{Best fitting parameters for our \SFRDzZ fit to TNG100 data.}
\tablehead{\colhead{dP/dZ param.} & \colhead{best fit} & \colhead{SFRD(z) param.} & \colhead{best fit} } 
%% All data must appear between the \startdata and \enddata commands
\startdata
$\mu_0$ &  0.025 &  $a$ &  0.02 \\
$\mu_z$ &  -0.048 &  $b$ &  1.48 \\
$\alpha_0$ &  -1.767 &  $c$ &  4.45 \\
$\omega_0$  & 1.125       &  $d$ &  5.90 \\
$\omega_z$ &  0.048 &   \\
\enddata
%sf_a_best, sf_b_best, sf_c_best,  sf_d_best = 0.02, 1.48, 4.45, 5.90
% sf_a =0.01687063881834458, sf_b =1.4834054063851878, sf_c =4.448574027958166, sf_d =5.903964702985274

@@

Testing if this works: I now changed something in the overleaf!
